### 2015-01-31 docs/report/serialization_transference.tex
Pointing to benchmark in spikes folder

\subsubsection{With 100000 elements}
The following is the code for the benchmark:
\bmcode{http://js-perf}{js_lang.tex}

These were the results:
\bmcode{Results with 100000 elements}{js_lang.tex}

\subsubsection{With 1000000 elements}
The following is the code for the benchmark:
\bmcode{http://js-perf}{js_lang.tex}

These were the results:
\bmcode{Results with 1000000 elements}{js_lang.tex}

>>>>

\subsubsection{With 100000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transferrable-vs-cloning}{../../spikes/1.2/transferrableVsCloning.js}

These were the results:
\bmchart{Results with 100000 elements}{../../spikes/1.2/transferrableVsCloning}

\subsubsection{With 1000000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/longer-transferrable-vs-cloning}{../../spikes/1.2/longerTransferrableVsCloning.js}

These were the results:
\bmchart{Results with 100000 elements}{../../spikes/1.2/longerTransferrableVsCloning}
